---
title: "Mileage per Hp/gear"
author: "Antonio Quintieri"
date: "March 15 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Understanding Gas Mileage vs hp/gear

Using the `mtcars` dataset, I 'm looking at the relationship of hp/gear and cylinders factors to gas mileage (`mpg`).

I plot hp/gear (`hp/gear`) vs. mileage (`mpg`) along the x/y axes, while the number of cylinders (`cyl`) as colors and the amount of horsepower (`hp`) as the size of an individual point in the plot.

## Conclusion
Mileage is related to # of cylnder and within each class of cylinder, hp/gear seems not having any correlation with mileage.
 
## Visualizing the Data

```{r plot, echo=FALSE}
suppressPackageStartupMessages(library(plotly))
plot_ly(data = mtcars, x = ~hp/gear, y = ~mpg, 
        color = ~as.factor(cyl), size = ~hp/gear,
        text = ~paste("Hp: ", hp/gear, '<br>MPG:', mpg),
        type = "scatter", mode = "markers") %>%
  layout(title = "Car Data: mileage vs hp/gear")
```

